``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)

### 2022-12-20 paper/04--otherLinearization.tex
...

\def\year{2022}\relax
%File: formatting-instructions-latex-2022.tex
%release 2022.1
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
% \usepackage{algorithm}
% \usepackage{algorithmic}
% \usepackage[noend]{algpseudocode}

%
% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
\usepackage{newfloat}
\usepackage{listings}
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
%\floatstyle{ruled}
%\newfloat{listing}{tb}{lst}{}
%\floatname{listing}{Listing}

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{xcolor}
\usepackage{booktabs} 
% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb} 
\usepackage{mathbbol}
\usepackage{tikz}
\usetikzlibrary{aiplans}

\scheme{SinglePrec}{0}{
	text = {\textbf{A}},
	pre  = {a}
}

\scheme{SingleAdd}{0}{
	text = {\textbf{B}},
	effs = { a}
}

\scheme{SingleDelete}{0}{
	text = {\textbf{C}},
	effs = { {{$\neg$}a} }
}

\scheme{SinglePrecAlt}{0}{
	text = {\textbf{D}},
	pre  = {a}
}

\scheme{SingleAddAlt}{0}{
	text = {\textbf{E}},
	effs = { a}
}

\scheme{PrimitiveA}{0}{
	text = {\textbf{A}},
	pre  = {a},
	effs = { {{$\neg$}a}, {b} }
}

\scheme{PrimitiveB}{0}{
	text = {\textbf{B}},
	pre = {b},
	effs = {{{$\neg$}b}, {c}}
}

\scheme{PrimitiveC}{0}{
	text = {\textbf{C}},
	pre = {c},
	eff = {{$\neg$}c}
}

\nocopyright
%
% PDF Info Is REQUIRED.
% For /Title, write your title in Mixed Case.
% Don't use accents or commands. Retain the parentheses.
% For /Author, add all authors within the parentheses,
% separated by commas. No accents, special characters
% or commands are allowed.
% Keep the /TemplateVersion tag as is
\pdfinfo{
/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
Planning Problems is Half the Job (to Getting them Solved More Efficiently))
%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
/Author (Anonymous)
/TemplateVersion (2022.1)
}

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai22.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash

%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
% \iffalse

\newtheorem{theorem}{Theorem}

\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)

\newcommand{\Add} {\ensuremath{\mathit{add}}}
\newcommand{\Del} {\ensuremath{\mathit{del}}}
\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}

%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}

%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}

\author {
    Submission
}
\affiliations{
    Anonymous
}
% \fi

%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\iffalse 
%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
\author {
    % Authors
    Anonymous

}
\affiliations {
    % Affiliations
    Anonymous
}
\fi

\title{``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)}

%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}

% REMOVE THIS: bibentry
% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
% \usepackage{bibentry}
% END REMOVE bibentry

\begin{document}
\input{00--macro.tex}
\maketitle

\begin{abstract} 
HTN planning is in general undecidable, yet there exist efficient
planning algorithms. An important subclass is that of totally ordered
HTN planning problems. Not only is this class decidable, but also easier
to handle algorithmically since tasks cannot interleave anymore.
Consequently, several specialized solvers exist, and dedicated tracks at
the International Planning Competition (IPC) in both 2020 and 2023. We
were able to show that almost all currently existing partially ordered
planning benchmarks can be turned into totally ordered ones without
sacrificing solvability. Establishing totally ordered problems in a
preprocessing technique thus allows to use planning systems, heuristics,
pruning techniques (etc.) that are only available for totally ordered
problems. This allows solving problems more efficiently and with
better-informed techniques, at the (little) cost of doing a
preprocessing technique. We show that in only a very few cases
linearization isn't possible, and in all others establishing a total
order pays off \emph{significantly}, thus establishing our technique as
a significant ingredient in the state of the art for solving partially
ordered HTN problems. As a side contribution, we identify a new class of
decidable (EXPTIME-complete) HTN problems, namely those where our
preprocessing technique is guaranteed to be solvability-preserving.
\end{abstract}

\section{Introduction}
% \input{01--intro.tex}
Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound. HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks. A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications. If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.

In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks. In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.

% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space. For some problems, such over-specification may remove all valid solutions.

Many problems might be naturally more suited to being modelled as POHTN problems. However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions. For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages. On the other hand, TOHTN planning is not expressive enough to model undecideable problems. Where this is possible, it results in lower worst-case solving time. Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.

Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case. % Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems. We prove that when certain criteria are met, it guarantees that at least one solution will be preserved. 
Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion. Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.

\section{Hierarchical Planning Formalism}
\input{02--htn.tex}

\section{Linearizing Grounded HTN Problems}
\input{03--linearization-ground.tex}

% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other. This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.

% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }

% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed. If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$. This is true for all possible tasks by simple induction over the decomposition process.

% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.

% Specifically, let $\sigma$ be the set of parameters for the method. Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$. Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.

% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects. For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects. % This is illustrated in Figure~\ref{CompoundPreEffForLifted}.

% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$. The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded. Only one linearized lifted method per partially-ordered lifted method is produced.

% For a grounded method, there are no parameters in a task or method. Methods decompose to specific actions, actions have preconditions and effects on specific state variables. We can then use these to produce a linearized grounded method per grounded method.

% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
% \begin{align*}
% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
% & \forall t \in T_P : \AddS(t) := \Add(t) \\
% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
% \end{align*}

% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects. Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.

%State-independent positive and negative effects (cf. their Def. 4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$

% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
% after every refinement of c but after at least one:
% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

% The set of executability-enabling states of c is
% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.

% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.

% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
% the precondition relaxation can make further refinements executable that produce
% effects that can not be achieved in the non-relaxed domain. 
% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.

% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o. refinements (ignoring executability of the refinement) $\langle a_0 ... a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.

% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
% In this paper, we will be utilising both of these, as seen in the next section.
%the precondition-relaxed possible effects, which may hold after at least one refinement of c.

%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
%f ∈ prec(ai) and there does not exist an action aj with
%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
%The exploitation of the relaxed preconditions and effects
%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates

@@

% \begin{algorithm}[h]
% 	\caption{Calculation of linearized methods}
% 	\label{alg:Algorithm1}
% 	\KwData{$(F, T_P, T_C, \delta, M)$}
% 	\KwResult{$(F, T_P, T_C, \delta, M)$}

% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
% 	{
% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
% 		$G \gets \singlePrec$ \\
% 		\label{alg:StartBuildGraph}
% 		\For{a $\in$ F}{  
% 			\For{$t \in T_m$}{
% 				\For{$t' \in T_m$}{
% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
% 				}
% 			} 
% 			\label{alg:EndBuildGraph}	
% 		}	
% 		\label{alg:StartCycleBreak}
% 		\While{$G$ has cycles in it}{
% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
% 		}
% 		\label{alg:EndCycleBreak}
% 		$\prec'$ = Any linearization of $G$ \\
% 		\label{alg:TopSort}
% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
% 		$M' = M' \cup  \{m'\}$ \\

% 	}
% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
% \end{algorithm}

From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:

 \begin{figure}[h]
 	\caption{Example of Desired Additional Orderings}
 	\label{fig:OrderingRules}
	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{Del}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{first}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em ,
					body = {right = 4em of Del} 
			};

@@

	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{Del}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of } 
			};

			\action{Prec}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of Del} 
			};

			\action{Add}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of Prec} 
		};

			\path[every node/.style={font=\sffamily\small}]
			(Prec) edge [->,bend right] node [left]  {} (Del);
			\end{tikzpicture}
			\caption{C deletes a fact in preconditions of A  -- so A before C}	
		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{Add}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{Prec}{SinglePrec,
			width  = 2.5em, 
			height = 2.5em, 
			pre length = 1em,
			eff length = 1em,
			body = {left = 4em of Add} 
			};

			\action{Del}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of Prec} 
			};

			\path[every node/.style={font=\sffamily\small}]
			(Del) edge [->, bend right] node [left]  {} (Add);
			\end{tikzpicture}
			\caption{B adds a fact that C deletes -- so C before B}
		\end{subfigure}
	} 
\end{figure}

@@

			\action{C}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second} 	
				%body = {below left = 2em and 2em of } 
			};

@@

			\action{C}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second} 	
				%body = {below left = 2em and 2em of } 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
		%	(A) edge [->,bend right] node [left]  {} (C)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}

%	\scalebox{0.75}{
%		\begin{subfigure}{7cm} 
%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
%			\label{fig:NotCycleBreaking}
%			\begin{tikzpicture}[auto,node distance=1.2cm,
%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

%			\action{B}{SingleAddAlt,
%				width  = 2.5em, 
%				height = 2.5em, 
%				pre length = 1em,
%				eff length = 1em 
%			};

%			\action{A}{SinglePrecAlt,
%				width  = 2.5em, 
%				height = 2.5em, 
%				pre length = 1em,
%				eff length = 1em,
%				body = {right = 4em of first} 		
%			};

%			\path[every node/.style={font=\sffamily\small}]
%			(B) edge [->,bend right] node [left]  {} (A);
%			\end{tikzpicture}

%			\caption{Resulting method ordering has no cycle}
%			
%		\end{subfigure}
%	}   
\end{figure}

% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase. Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.

\section{Theoretical Properties of Linearization Result}

We now discuss the implications of the above-described linearization procedure.

\begin{theorem}\label{thm:Runtime}
	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
\end{theorem}
\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
	Let $|T|$ = $|T_P| + |T_C|$.

	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,

	To calculate $\PreS, \AddS, \DelS$ for each task $t$. We explore it's compound sub-tasks until we collect all primitive tasks. Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree. This is obviously polynomial in terms of $|T|$. %This provides an upper limit of $(3 * |F| * |T_p|) + T_C$. This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$. % we explore all poss (at most $|T_C|$)

	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method. Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.

	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.

	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time. % and $\mathcal{O}(V)$ in space.  
	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.

	So the algorithm takes polynomial time. 
\end{proof}

\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

>>>>

@@

From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.

 \begin{figure}[h]
 	\caption{Example of Desired Additional Orderings}
 	\label{fig:OrderingRules}
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{first}{SingleAdd,
				width  = 2.5em,
				height = 2.5em,
				pre length = 1em,
				eff length = 1em
			};

@@

		\end{subfigure}
	}
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{A}{SingleDelete,
				width  = 2.5em,
				height = 2.5em,
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of }
			};

			\action{B}{SinglePrec,
				width  = 2.5em,
				height = 2.5em,
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of A}
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{C deletes a fact in preconditions of A  -- so A before C}
		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{4.5cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{A}{SingleAdd,
				width  = 2.5em,
				height = 2.5em,
				pre length = 1em,
				eff length = 1em
			};

			\action{B}{SingleDelete,
				width  = 2.5em,
				height = 2.5em,
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of A}
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->, bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{B adds a fact that C deletes -- so C before B}
		\end{subfigure}
	}
\end{figure}

@@

			\action{C}{SingleDelete,
				width  = 2.5em,
				height = 2.5em,
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second}
			};

@@

			\action{C}{SingleDelete,
				width  = 2.5em,
				height = 2.5em,
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second}
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}

		\end{subfigure}
	}
\end{figure}
